Hydra Battles and Cie

### 2021-07-15 doc/part-hydras.tex
more proofs by refinement

    \end{project}
    \section{A variant for hydra battles}

>>>>

    \section{A refinement of \texttt{E0} : an ordinal notation for \texorpdfstring{$\omega^\omega$}{omega\^omega}}

    In Module   \href{https://github.com/coq-community/hydra-battles/blob/master/theories/ordinals/OrdinalNotations/OmegaOmega.v}{theories/ordinals/OrdinalNotations/OmegaOmega.v},
we represents ordinals below $\omega^\omega$ by list of pairs of natural numbers. we establish this representation as a \emph{refinement} of the data types we used to represent ordinals less than $\epsilon_0$. Thus, many properties like well-foundedness of $<$ and associativity of $+$,  of this ordinal notations have very short proofs.

%ici
    \section{A variant for hydra battles}
